Similar Sentence Detection Using Locality Sensitive Hashing Technique on Wikipedia

### 2013-11-03 article/article-draft.tex
Added a more generic cluster scoring method to TemplateCluster class

By manually counting a small sample of 2094 output clusters, we came up with a breakdown of sentence types shown in Table 1.

\begin{table}
\centering
\caption{Sentence Breakdown Counts}
\begin{tabular}{| l | c | c |}
\hline
Factual Drift & 121 & 5.78\% \\ \hline
Template & 632 & 30.18\% \\ \hline
Reference & 7 & 0.33\% \\ \hline      
Copy Edit & 283 & 13.51\% \\ \hline
Identical & 948 & 45.27\% \\ \hline
Other & 103 & 2.92\% \\ \hline
\hline
\end{tabular}
\end{table}

@@

Applying the score to our hand-classified clusters shows us that this score does separate between template and non-template word. (Everything that isn't in the Template class is considered a non-Template for the binary classification exercise.)

N lines: 3496074
N clusters: 1151620
N identical clusters: 666212
N template clusters: 55430
N other clusters: 20745
N other pair clusters: 407963
N species clusters: 1270

N lines: 3496074
N clusters: 1151620
N identical clusters: 666212
N template clusters: 244660
N template sentences: 1116932
N other clusters: 20745
N other pair clusters: 218840
N species clusters: 1163
^C

After applying the score to the entire set of wiki clusters (with a score threshold of .6), there are 244,660 template clusters and 906,960 non-template clusters, including 666,212 identical clusters. The template clusters contain 1,116,932, and the non-template

>>>>

By manually counting a small sample of 2094 output clusters, we came up with a breakdown of sentence types shown in Table \ref{counts}.

\begin{table}
\centering
\caption{Sentence Breakdown Counts}
\begin{tabular}{| l | c | c |}
\hline
Factual Drift & 121 & 5.78\% \\ \hline
Template & 632 & 30.18\% \\ \hline
Reference & 7 & 0.33\% \\ \hline      
Copy Edit & 283 & 13.51\% \\ \hline
Identical & 948 & 45.27\% \\ \hline
Other & 103 & 2.92\% \\ \hline
\hline
\end{tabular}
\label{counts}
\end{table}

@@

Applying the score to our hand-classified clusters shows us that this score does separate between template and non-template clusters. (Everything that isn't in the Template class is considered a non-Template for the binary classification exercise.) See Figure \ref{heuristic}.

After applying the score to the entire set of wiki clusters (with a score threshold of .6), there are 244,660 template clusters and 906,960 non-template clusters, including 666,212 identical clusters. The template clusters contain 1,116,932 sentences, and the non-template clusters contain 1,244,196.
